### 2020-08-07 thesis/thesis.tex
gen intro

% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetIntroName{{General Introduction}} % To review

@@

Ecological connectivity is the extent to which the landscape supports the movements of organisms \citep{gonzalez_spatial_2017}, and is paramount for the resilience of both populations and ecosystem services \citep{mitchell_monteregie_2015} in heterogeneous and fragmented landscapes. Land use changes such as urban sprawl can cause deforestation, fragmenting habitats, and slowly eroding ecological connectivity. Many urban landscapes are experiencing uncontrolled urban sprawl and have suffered losses in connectivity and ecosystem services in consequence. Examples include cities like Barcelona \citep{marulli_gis_2005}, New York City \citep{mcphearson_urban_2014}, and also Montreal \citep{dupras_urban_2015}.  The drivers behind those land use changes are complex and understanding them is an obstacle to conservation planning  \citep{worboys_connectivity_2010}, including connectivity conservation planning. \\
Connectivity conservation planning (CCP), refers to the enterprise that engages multiple actors such as academics, NGOs, governmental bodies at different scales and in a common goal to conserve the ecological connectivity of the landscape. CCP methods usually entails modelling connectivity of the landscape of interest and using a prioritization method to determine conservation priorities, and modify land use practices to conserve or improve connectivity. This study constitutes a contribution to an ongoing effort of CCP in Montérégie, in southern Quebec. In the following, we introduce the study region and describe previous efforts of CCP. We then point out ways in which CCP methods can be improved and how this thesis contributes to doing so. \\

\subsection*{\textit{Study Region and previous efforts}}

@@

Deriving insight from these contributions, multiple stakeholders have become mobilized to set connectivity conservation goals for the region. A number of Non-Governmental NGOs have designed corridor networks over their jurisdiction, with varying degrees of inputs from previous scientific work. For instance, Nature Action Québec (NAQ) and the Centre de la Nature du Mont Saint Hilaire (CDN), but also the Centre d'interprétation du milieu écologique du Haut-Richelieu (CIME), and Appalachian Corridors (CA), which has been pioneering the approach in the region (although their jurisdiction is at the margin of Monteregie, in Estrie). These associations are now beginning to work together to design science-driven connectivity conservation plans for the whole region, and are in need of decision tools in that regard. They are concerned with the social acceptability of conservation, and with resilience of their plan to future land use and climate change. \\

\subsection*{\textit{Limitations of current CCP methods}}

@@

Next, we introduce the three key conceptual themes of the thesis: connectivity modelling, land use change modelling, and participatory methods. \\

\subsection*{\textit{Connectivity modelling}}

@@

This thesis makes use of circuit theory to estimate change to potential functional connectivity in 5 umbrella species, under a certain number of land use change scenarios. Next, we introduce land use change modelling. \\

\subsection*{\textit{Land use change modelling}}

@@

This thesis therefore makes use of a hybrid modeling approach. We combine this model with scenarios who were derived from a participatory method, which we introduce next. We end with simple predictions as to the results of our modelling effort. \\

\subsection*{\textit{Participatory methods in Connectivity Conservation}}
CCP researchers are increasingly recognizing landscapes are social ecological systems. A social-ecological system (SES, \cite{ostrom_general_2009}) can be conceived  as the set of human and non-human actors, the set of natural habitats they inhabit and resources and use, and the set of interactions that are maintained between all the components of the system. SESs thus form complex and integrated aggregates of interactions \citep{hinkel_enhancing_2014}. Those interactions also impact governance, the process by which actors in power establish rules and laws \citep{bissonnette_comparing_2018}. Conservation and land use change are inherently social practices, with repercussions of both social and ecological nature. Connectivity conservation science is therefore called to take an increasingly social-ecological approach to modelling and planning. \\

@@

We can therefore derive different predictions as to how connectivity will be affected for each species under our model. Three main predictions can be made. First, under the BAU scenario, we can expect that our land use change model will simulate an decrease in connectivity change for our focal species. We can also expect connectivity to maintain itself under the Reforestation scenario. Finally. We can expect climate change to impact more strongly species that prefer coniferous  and mixed forest types.

@@

%\ETDAppendix{References}{
%\printbibliography
%}
\printbibliography[heading=bibintoc, section=0, title={General Bibliography \hspace{1em}}]

>>>>

% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetIntroName{{General Introduction}}

@@

Ecological connectivity is the extent to which the landscape supports the movements of organisms \citep{gonzalez_spatial_2017}, and is paramount for the resilience of both populations and ecosystem services \citep{mitchell_monteregie_2015} in heterogeneous and fragmented landscapes. Land use changes such as urban sprawl can cause deforestation, fragmenting habitats, and slowly eroding ecological connectivity. Many urban landscapes are experiencing uncontrolled urban sprawl and have suffered losses in connectivity and ecosystem services in consequence. Examples include cities like Barcelona \citep{marulli_gis_2005}, New York City \citep{mcphearson_urban_2014}, and also Montreal \citep{dupras_urban_2015}.  The drivers behind those land use changes are complex and understanding them is an obstacle to conservation planning  \citep{worboys_connectivity_2010}, including connectivity conservation planning. \\
Connectivity conservation planning (CCP), refers to the enterprise that engages multiple actors such as academics, NGOs, governmental bodies at different scales and in a common goal to conserve the ecological connectivity of the landscape. CCP methods usually entails modelling connectivity of the landscape of interest and using a prioritization method to determine conservation priorities, and modify land use practices to conserve or improve connectivity. This study constitutes a contribution to an ongoing effort of CCP in Montérégie, in southern Quebec. In the following, we introduce the study region and describe previous efforts of CCP. We then point out ways in which CCP methods can be improved and how this thesis contributes to doing so. \\ \vspace{2em}

\subsection*{\textit{Study Region and previous efforts \\ \vspace{1em}}}

@@

Deriving insight from these contributions, multiple stakeholders have become mobilized to set connectivity conservation goals for the region. A number of Non-Governmental NGOs have designed corridor networks over their jurisdiction, with varying degrees of inputs from previous scientific work. For instance, Nature Action Québec (NAQ) and the Centre de la Nature du Mont Saint Hilaire (CDN), but also the Centre d'interprétation du milieu écologique du Haut-Richelieu (CIME), and Appalachian Corridors (CA), which has been pioneering the approach in the region (although their jurisdiction is at the margin of Monteregie, in Estrie). These associations are now beginning to work together to design science-driven connectivity conservation plans for the whole region, and are in need of decision tools in that regard. They are concerned with the social acceptability of conservation, and with resilience of their plan to future land use and climate change. \\ \vspace{2em}

\subsection*{\textit{Limitations of current CCP methods \\ \vspace{1em}}}

@@

Next, we introduce the three key conceptual themes of the thesis: connectivity modelling, land use change modelling, and participatory methods. \\ \vspace{10em}

\subsection*{\textit{Connectivity modelling \\ \vspace{1em}}}

@@

This thesis makes use of circuit theory to estimate change to potential functional connectivity in 5 umbrella species, under a certain number of land use change scenarios. Next, we introduce land use change modelling. \\ \vspace{2em}

\subsection*{\textit{Land use change modelling \\ \vspace{1em}}}

@@

This thesis therefore makes use of a hybrid modeling approach. We combine this model with scenarios who were derived from a participatory method, which we introduce next. We end with simple predictions as to the results of our modelling effort. \\ \vspace{2em}

\subsection*{\textit{Participatory methods in Connectivity Conservation \\ \vspace{1em}}}

CCP researchers are increasingly recognizing landscapes are social ecological systems. A social-ecological system (SES, \cite{ostrom_general_2009}) can be conceived  as the set of human and non-human actors, the set of natural habitats they inhabit and resources and use, and the set of interactions that are maintained between all the components of the system. SESs thus form complex and integrated aggregates of interactions \citep{hinkel_enhancing_2014}. Those interactions also impact governance, the process by which actors in power establish rules and laws \citep{bissonnette_comparing_2018}. Conservation and land use change are inherently social practices, with repercussions of both social and ecological nature. Connectivity conservation science is therefore called to take an increasingly social-ecological approach to modelling and planning. \\

@@

We can therefore derive different predictions as to how connectivity will be affected for each species under our model. Three main predictions can be made. First, under the BAU scenario, we can expect that our land use change model will simulate an decrease in connectivity change for our focal species. We can also expect connectivity to maintain itself under the Reforestation scenario. Finally. We can expect climate change to impact more strongly species that prefer coniferous  and mixed forest types. \\

@@

%\ETDAppendix{References}{
%\printbibliography
%}
\printbibliography[heading=bibintoc, section=0, title={General Bibliography \vspace{1em}}]
